quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-18 paper-quollr.tex
Updated version with scratch codes

\begin{itemize}
\tightlist
\item
  basic example
\end{itemize}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-35-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-40-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-43-1.pdf}

@@

\begin{verbatim}
#> Calculating PHATE...
#>   Running PHATE on 824 observations and 8 variables.
#>   Calculating graph and diffusion operator...
#>     Calculating KNN search...
#>     Calculating affinities...
#>   Calculated graph and diffusion operator in 0.01 seconds.
#>   Calculating optimal t...
#>     Automatically selected t = 22
#>   Calculated optimal t in 0.49 seconds.
#>   Calculating diffusion potential...
#>   Calculated diffusion potential in 0.38 seconds.
#>   Calculating metric MDS...
#>   Calculated metric MDS in 7.83 seconds.
#> Calculated PHATE in 8.72 seconds.
\end{verbatim}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-50-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-55-1.pdf}

@@

>>>>

\begin{itemize}
\tightlist
\item
  basic example
  --\textgreater{}
\end{itemize}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-39-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-42-1.pdf}

@@

@@

\begin{verbatim}
#> Calculating PHATE...
#>   Running PHATE on 824 observations and 8 variables.
#>   Calculating graph and diffusion operator...
#>     Calculating KNN search...
#>     Calculating affinities...
#>   Calculated graph and diffusion operator in 0.01 seconds.
#>   Calculating optimal t...
#>     Automatically selected t = 22
#>   Calculated optimal t in 0.26 seconds.
#>   Calculating diffusion potential...
#>   Calculated diffusion potential in 0.36 seconds.
#>   Calculating metric MDS...
#>   Calculated metric MDS in 8.01 seconds.
#> Calculated PHATE in 8.64 seconds.
\end{verbatim}

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-48-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-52-1.pdf}

@@

@@

\includegraphics{paper-quollr_files/figure-latex/unnamed-chunk-60-1.pdf}
